\documentclass[8pt,a4paper]{moderncv}

% Themes
\moderncvstyle{casual}
\moderncvcolor{blue}
\usepackage[scale=0.8, top=1cm, bottom=3cm]{geometry}

% Personal data
\firstname {Kevin}
\lastname {Hwang}
\title{Senior iOS Engineer}
\address{2621 Sacramento St.}{Berkeley, CA 94702}
\phone[mobile]{(909)~802~8999}
\email{k3vinhwang@gmail.com}
\homepage{www.kevinhwang.net}
\social[linkedin]{k3vinhwang}
\social[twitter]{k3vinhwang}
\social[github]{khwang}

\begin{document}
\makecvtitle

\vspace*{-2\baselineskip}

\section{Education}
\cventry{2009-2012}{Bachelor of Science in Electrical Engineering and Computer Sciences}{University of California, Berkeley}{Berkeley}{}{Overall GPA: 3.385}

\section{Work}
\cventry{Summer 2012-Present}{Scribd, Inc.}{Senior iOS Engineer}{San Francisco}{}{Currently on the mobile team, with past experience as a full-stack developer. Sample projects include revamping the entire Search experience for the 4.0 release, architecting the transition to a credit-based system for audiobooks, and building infrastructure to both import book ratings, reviews, and popularity data as well as displaying it.}

\cventry{Summer 2011}{University of California, Berkeley}{Undergraduate Teaching Assistant}{Berkeley}{}{Instructed students in the introductory course in computer science by leading a discussion section and a lab section. Wrote and graded the exams.}

\section{Projects}

\cventry{April 2015}{Persimmon}{A text analysis project. Implemented Flipboard's text summarizer}{}{}{\url{https://github.com/Radahika/Persimmon}}

\cventry{January 2015}{Saguaro}{A website for getting the most bang for your buck at Taco Bell. Input the amount of money you have, and receive a list of the items you should buy to maximize your calories}{}{}{\url{https://github.com/khwang/saguaro}}

\cventry{September 2012}{Strawberry}{A music visualizer utilizing the HTML5 Audio API and ThreeJS, for WebGL. Third place winner at HackJam Fall 2012}{}{}{\url{https://github.com/khwang/strawberry}}

\cventry{April 2012}{Gala}{Learn to program by commanding an army of robots in space. Built for the Y Combinator Summer 2012 interview}{}{}{\url{https://github.com/khwang/gala}}

\section{Activities}

\cventry{}{Eta Kappa Nu Honors Society}{Electrical and computer engineering honors society}{}{}{}

\cventry{}{Computer Science Undergraduate Association}{}{}{}{}

\cventry{}{Lindy on Sproul}{Swing dancing instructor, performer, and website coordinator}{}{}{}

\cventry{}{Hackers at Berkeley}{Founding officer for a club that promotes hacking culture}{}{}{}

\cventry{}{Berkeley Dancer's Den}{Web Designer, Swing DJ}{}{}{}

\section{Skills}
\cventry{}{Languages}{}{}{}{\begin{itemize}
		\item Preferred: Swift, Objective-C, Javascript, Ruby, Scheme
		\item Familiarity: Python, CoffeeScript, Java, C, C++, HTML5/CSS3
	\end{itemize}}{}
	
  \cventry{}{Frameworks}{}{}{}{iOS, Ruby on Rails, NodeJS, Socket.IO, jQuery, Web.py}{}

\end{document}

\vspace*{-2\baselineskip}
